SAT Solving for Vesicle Traffic Systems in Cells

### 2017-10-01 paper/abstract.tex
added new formula

In biology, there are several questions that translate to combinatorial
search. For example, vesicle traffic systems that move cargo within
eukaryotic cells have been proposed to exhibit several graph properties
such as three connectivity. These properties are consequences of underlying
biophysical constraints. A natural question for biologists is: what are all
possible networks for various combinations of those properties? In this
paper, we present novel SAT encodings of the properties over vesicle traffic
systems and a tool that searches for the networks that satisfies the
properties using SAT solvers. In our experiments, we show that our tool
can search for networks of sizes that are considered to be relevant by
biologists.

>>>>

In biology, there are several questions that translate to combinatorial
search. For example, vesicle traffic systems that move cargo within
eukaryotic cells have been proposed to exhibit several graph properties
such as three connectivity. These properties are consequences of underlying
biophysical constraints. A natural question for biologists is: what are the
possible networks for various combinations of those properties? In this
paper, we present novel SMT based encodings of the properties over vesicle traffic
systems and a tool that searches for the networks that satisfies the
properties using SMT solvers. In our experiments, we show that our tool
can search for networks of sizes that are considered to be relevant by
biologists.

### 2017-10-01 paper/encoding.tex
added new formula

In this section, we will formally define VTSs as a labeled graph
and the discussed conditions on the graphs.
%
Subsequently, we will present the SAT encoding of the search problems
for the graphs that satisfy the conditions.

@@

We translate the search problem into a Boolean satisfiability
problem and use SAT solvers to find the satisfying VTSs.
%
We will first present the variables used to encode the
VTSs and the properties.
%
Afterwards, we will present the constraints corresponding to the
properties.

@@

\subsection{SAT problems for different variants}
%\ankit{Bring model variant table here}

>>>>

In this section, we will formally define VTSs as a labeled graph
and the discussed conditions on the graphs.
%
Subsequently, we will present the SMT encoding of the search problems
for the graphs that satisfy the conditions.

@@

We translate the search problem into a Boolean satisfiability
problem and use SMT solvers to find the satisfying VTSs.
%
We will first present the variables used to encode the
VTSs and the properties.
%
Afterwards, we will present the constraints corresponding to the
properties.

@@

\subsection{Complete formula}
The complete QBF looks like the following.
\begin{align}
\exists \, e_{i,j,q} \forall \,d_{i,j,q}, r^{\prime}_{i,j,q} \, (D1 \land D2 \land D3 \land D4)  \, \land \notag\\  \forall\, n_{i,k}, a_{i,k}, e_{i,j,k,q}, b_{i,j,k,q}, r_{i,j,k}, p_{k,k^{\prime}} \, \neg (V1 \land V2 \land ... V8 \land A_{n} \land A_{e})  \label{eq:final}
\end{align}

\subsection{SMT problems for different variants}
%\ankit{Bring model variant table here}
